SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-02 docs/questioning.tex
more on tainting

Most of the aforementioned frameworks, involve
several deployment issues since they
require significant source modifications by the web
developers in order to introduce their policies.

@@

There are different implementations of these approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}). However, this is a simplistic
approach that may lead to many false positives.
{\sc csse}~\cite{PB05} and the scheme by {\it Xu et al.}~\cite{XBS06}
apply further checks when they identify that tainted data
have reached a sink. In particular, {\sc csse} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and other. When tainted data reaches a sink {\sc csse} performs
syntactic checks it based on the aforementioned metadata
(locus {\sc z}).

>>>>

Most of the aforementioned frameworks, involve
several deployment issues since they
require significant source modifications by the web
developers in order to introduce policies.

@@

There are different implementations of these approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}). However, this is a simplistic
approach that may lead to many false positives.
{\sc csse}~\cite{PB05} and the system by {\it Xu et al.}~\cite{XBS06}
apply further checks when they identify that tainted data
have reached a sink. In particular, {\it Xu et al.}~\cite{XBS06}
tracks taint information at the level of bytes in memory.
To distinguish between legitimate and malicious uses
of untrusted data that reach a sink,
they search the data for suspicious symbols by using
regular expressions. {\sc csse} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and other. When tainted data reaches a sink {\sc csse} performs
syntactic checks it based on the aforementioned metadata
(locus {\sc z}). {\it Xu et al.}~\cite{XBS06}
have proposed a 
In the case of {\sc dsl}-driven injection attacks,
the above implementations can be efficient. However, this
does not apply in the case of JavaScript injection.
Currently, with the wide use of JavaScript these mechanisms
would produce numerous false alarms because instead
of checking for tainted variables ``in" scripts,
they look inside {\sc html} responses ``for" scripts.
